\titleNameLong{}

### 2015-12-07 FinalProject/Tex/paper/paper.tex
converted design section from list to subsections
expanded subsections into sections

The remainder of this survey is organized as follows. Section
\ref{sec:architecture} provides a brief architectural overview of GPUs. Section
\ref{sec:challenges} elaborates on the challenges specific to GPGPU
applications. Section \ref{sec:research} summarizes and discusses several
current areas of research related to GPGPU. Section \ref{sec:conclusions}
concludes the survey.

% \section{Background}
% \subsection{GPU History}
% TODO
% \subsection{GPGPUs and Current State}
% TODO
% \subsection{Applications}
% TODO

@@

\section{New Designs} \label{sec:research}
\begin{itemize}
\item Warp compression stuff
  \begin{itemize}
  \item Assist warps (CABA)
  \item Warped Compression
  \end{itemize}
\item Dynamic tuning
  \begin{itemize}
  \item Coordinated warp scheduling (CAWA)
  \item Dynamic Thread Block Launch (DTBL)
  \item Equalizer
  \item Fine-grain Hardware Worklists (HWWL)
  \item Variable Warp Size (VWS)
  \end{itemize}
\item CPU/GPU contention, NoC
  \begin{itemize}
  \item Managing Concurrency in Heterogeneous
  \end{itemize}
\item Compiler/SW-only design
  \begin{itemize}
  \item Divergence Management
  \item Locality Aware Mapping
  \item (x) WeakBehaviorProgrammingAssumptions
  \end{itemize}
\end{itemize}

>>>>

The remainder of this survey is organized as follows. Section
\ref{sec:architecture} provides a brief architectural overview of GPUs. Section
\ref{sec:challenges} elaborates on the challenges specific to GPGPU
applications. Section \ref{sec:dynamic} discusses various dynamic approaches to
scheduling and warp configurations. Section \ref{sec:memory} talks specifically
about reducing memory contention. Section \ref{sec:software} is a discussion of
a few software and compiler solutions to the challenges of GPGPU. Section
\ref{sec:conclusions} concludes the survey.

@@

\section{Dynamic Warp Scheduling and Hardware Tuning} \label{sec:dynamic}
\subsection{Assist warps (CABA)}
This section left as an exercise to the reader
\subsection{Coordinated warp scheduling (CAWA)}
This section left as an exercise to the reader
\subsection{Dynamic Thread Block Launch (DTBL)}
This section left as an exercise to the reader
\subsection{Equalizer}
This section left as an exercise to the reader
\subsection{Fine-grain Hardware Worklists (HWWL)}
This section left as an exercise to the reader
\subsection{Variable Warp Size (VWS)}
This section left as an exercise to the reader

\section{Reducing Memory Contention} \label{sec:memory}
\subsection{Warped Compression}
This section left as an exercise to the reader
\subsection{Managing Concurrency in Heterogeneous (CPU/GPU NoC contention)}
This section left as an exercise to the reader

\section{Compiler/SW-only design} \label{sec:software}
\subsection{Divergence Management}
This section left as an exercise to the reader
\subsection{Locality Aware Mapping}
This section left as an exercise to the reader
\subsection{(x) WeakBehaviorProgrammingAssumptions}
This section left as an exercise to the reader
